Conversations in time: interactive visualization to explore structured temporal data

### 2020-07-28 tsibbletalk.Rmd
draft on plotly.js react method

* Transform and send newly-transformed data via server, without updating anything else (e.g. layout and graphical elements), to avoid completely redrawing. Performance.
* Double dispatch

>>>>

Transformed data generally requires redrawing the plot, and worsen the performance of shiny. This shiny module directly manipulate the underlying data with the `plotly.js` react method. Only transformed data is sent to the server side, while keeping the rest configuration unchanged (e.g. layout and graphical elements), for the performance reason. Users will not experience an obvious delay when the slider input is changed.

### 2020-07-28 tsibbletalk.tex
draft on plotly.js react method

\begin{itemize}
\tightlist
\item
  Transform and send newly-transformed data via server, without updating
  anything else (e.g.~layout and graphical elements), to avoid
  completely redrawing. Performance.
\item
  Double dispatch
\end{itemize}

>>>>

Transformed data generally requires redrawing the plot, and worsen the
performance of shiny. This shiny module directly manipulate the
underlying data with the \texttt{plotly.js} react method. Only
transformed data is sent to the server side, while keeping the rest
configuration unchanged (e.g.~layout and graphical elements), for the
performance reason. Users will not experience an obvious delay when the
slider input is changed.
